---
title: "Mark Brown Homework 1"
author: "Mark Brown"
date: "September 22, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Question 1

```{r, echo=FALSE, include=FALSE}
library(tidyverse)
library(quantmod)
library(fBasics)


```

Downloading the data

```{r}
##1

getSymbols('aapl',from='2000-01-01', to = '2016-12-31')
getSymbols('ibm',from='2000-01-01', to = '2016-12-31')
getSymbols('msft',from='2000-01-01', to = '2016-12-31')
getSymbols('intc',from='2000-01-01', to = '2016-12-31')
getSymbols('amzn',from='2000-01-01', to = '2016-12-31')


```

1.a Calculating Daily Returns
```{r}
#1a
d_aapl<-dailyReturn(AAPL)
d_ibm<-dailyReturn(IBM)
d_msft<-dailyReturn(MSFT)
d_intc<-dailyReturn(INTC)
d_amzn<-dailyReturn(AMZN)
```

1.b. Calculating Daily Log Returns

```{r}

#1b
l_aapl<-na.trim(diff(log(AAPL$AAPL.Adjusted)))
l_ibm<-na.trim(diff(log(IBM$IBM.Adjusted)))
l_msft<-na.trim(diff(log(MSFT$MSFT.Adjusted)))
l_intc<-na.trim(diff(log(INTC$INTC.Adjusted)))
l_amzn<-na.trim(diff(log(AMZN$AMZN.Adjusted)))
```

1.c. Calculating Annual Returns

```{r}
#1c

a_aapl<-annualReturn(AAPL)
a_ibm<-annualReturn(IBM)
a_msft<-annualReturn(MSFT)
a_intc<-annualReturn(INTC)
a_amzn<-annualReturn(AMZN)


```

#Question 2

Preparing the data for the summary table
```{r}


Table<-function(x){
    output<- vector()
    for (i in seq_along(d_stocks)){
   output[1]<- mean(x)
   output[2]<-  sd(x)
   output[3]<-  kurtosis(x)
   output[4]<-  skewness(x)
   return(output)
   print(output)
}
}

d_stocks<-cbind.data.frame(d_aapl,d_ibm,d_msft,d_intc,d_amzn)
colnames(d_stocks)<-c("aapl","ibm","msft","intc","amzn")

l_stocks<-cbind.data.frame(l_aapl,l_ibm,l_msft,l_intc,l_amzn)
colnames(l_stocks)<-c("aapl","ibm","msft","intc","amzn")

Apple<-Table(d_stocks$aapl)
Ibm<-Table(d_stocks$ibm)
Microsoft<-Table(d_stocks$msft)
Intel<-Table(d_stocks$intc)
Amazon<-Table(d_stocks$amzn)

Apple1<-Table(l_stocks$aapl)
Ibm1<-Table(l_stocks$ibm)
Microsoft1<-Table(l_stocks$msft)
Intel1<-Table(l_stocks$intc)
Amazon1<-Table(l_stocks$amzn)

table<-cbind.data.frame(Apple,Ibm,Microsoft,Intel,Amazon)
table1<-cbind.data.frame(Apple1,Ibm1,Microsoft1,Intel1,Amazon1)
colnames(table1)<-c('Apple','Ibm','Microsoft','Intel','Amazon')
Summary_table<-rbind.data.frame(table,table1)

rownames(Summary_table)<-c('Mean','SD','Kurt','Skew','L-Mean','L-SD','L-Kurt','L-Skew')
```

Summary Table of the Stocks

```{r}

Summary_table


```

#Question 3

Here are the stats for an unweighted portfolio.

```{r}

daily<-cbind(d_aapl, d_ibm, d_msft, d_intc, d_amzn)

portfolio<-rowMeans(daily)

basicStats(portfolio)


```


#Question 4

Normal test for Apple


```{r}

l_port<-log(portfolio+1)

normalTest(d_aapl,method = 'jb')

```

Normal test for IBM

```{r}

normalTest(d_ibm,method = 'jb')

```

Normal test for Microsoft

```{r}

normalTest(d_msft,method = 'jb')
```

Normal test for Intel

```{r}

normalTest(d_intc,method = 'jb')

```

Normal Test for Amazon

```{r}

normalTest(d_amzn,method = 'jb')

```

Normal test for an unweighted portfolio

```{r}

normalTest(portfolio,method = 'jb')

```

Normal test for the log of Apple

```{r}

normalTest(l_aapl,method = 'jb')

```

Normal test for the log of IBM 


```{r}

normalTest(l_ibm,method = 'jb')

```

Normal test for the log of Microsoft

```{r}

normalTest(l_msft,method = 'jb')

```

Normal test for the log of Intel

```{r}

normalTest(l_intc,method = 'jb')

```

Normal test for the log of Amazon

```{r}

normalTest(l_amzn,method = 'jb')

```

Nomal test for the log of an unweighted portfolio.


```{r}

normalTest(l_port,method = 'jb')

```




